Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-22 cvpr2018.tex

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
 \begin{equation}
 \label{game}
 \begin{split}
  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[log D(x)] +  \\
					  &\mathbb{E}_{z\sim p_{z}}[log (1-D(G(z)))]		   
 \end{split}
 \end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-log(D(G(z)))$ rather than $log(1-D(G(z)))$, namely, the $log(D)$ trick.

@@

Given a pair of image and text embedding pair $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer the $x$  to an image code $Code(x)$. $Code(x)$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}

@@

 Given an input consisting of a mini-batch of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. 
 The loss function of the matching aware discriminator are summarized as:
  \begin{equation}
  \label{matchignloss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D( x,  \psi_t) ) ] +  0.5*(\\
					  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D(x, \psi_{\hat{t}} )  ] +\\
					  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D(\hat{x}, \psi_t) ) ] 
  \end{split}
  \end{equation}
This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
  \begin{equation}
  \label{discoss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D_{pair}( x,  \psi_t) ) ] + 0.5*( \\
  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D_{pair}(\hat{x}, \psi_t) ) ] + \\
  & \mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - \\
  & \mathbb{E}_{t \sim p_{data}}[\log( D_{img}(\hat{x}) )]
  \end{split}
  \end{equation}
\textcolor{red}{equations needs to be verified, just a rough place holder}

@@

\begin{algorithm}
	\caption{Counting mismatches between two packed \DNA{} strings
		\label{alg:packed-dna-hamming}}
	\begin{algorithmic}[1]
		\Require{$x$ and $y$ are packed \DNA{} strings of equal length $n$}
		\Statex
		\Function{Distance}{$x, y$}
		\Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
		\Let{$\delta$}{$0$}
		\For{$i \gets 1 \textrm{ to } n$}
			\If{$z_i \neq 0$}
				\Let{$\delta$}{$\delta + 1$}
			\EndIf
		\EndFor
		\State \Return{$\delta$}
		\EndFunction
	\end{algorithmic}
\end{algorithm}

>>>>

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
 \begin{equation}
 \label{game}
 \begin{split}
  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
 \end{split}
 \end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.

@@

The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$. $Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}

@@

 Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
 $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.

The loss function of the matching aware discriminator are summarized as:
  \begin{equation}
  \label{matchignloss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
  \end{split}
  \end{equation}
This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
  \begin{equation}
  \label{discoss}
  \begin{split}
  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
  \end{split}
  \end{equation}
\textcolor{red}{equations needs to be verified, just a rough place holder}

@@

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]

 		\For{$i \gets 1 \textrm{ to } S$ }
 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}

 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $

 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}

 		\EndFor

 	\end{algorithmic}
 \end{algorithm}

%\begin{algorithm}
%	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.   
%		\label{alg:gan-train}}
%	\begin{algorithmic}[1]
%		\Input{sample a minibatch of images, $x$, matching text description $t$, mis-matching $\hat{t}$,
%			}
%		\For{$i \gets 1 \textrm{ to } S$}
%			$z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
%			\State $\hat{x_1}$=$G(z_1, \psi_t)$ \Comment{Forward through $G$ using matching text embedding}
%			\STATE {$\hat{x_2}$}{$G(z_2, \psi_\hat{t})$} \Comment{Forward through $G$ using mis-matching text embedding}
%			
%			\STATE {$d_r$}{$D_{pair}(x, \psi_t)$} \Comment{(real image, matching text)}
%			\STATE {$d_m$}{$D_{pair}(x, \psi_\hat{t})$} \Comment{(real image, mis-matching text)}
%			\STATE {$d_f$}{$D_{pair}(\hat{x_1}, \psi_t)$} \Comment{(fake image, matching text)}
%			\STATE {$s_r$}{$D_{img}(x)$} \Comment{Forward through $D_{img}$ with $x$}
%			\STATE {$s_1$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_1}$}
%			\STATE {$s_2$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_2}$}
%			\STATE {$\mathcal{L}_{D}$}{$(d_r-1)^2 + (s_r-1)^2 + (d_m + d_f + s_1 + s2)/2 $} 
%			\STATE {$\mathcal{L}_{G}$}{$((d_f -1)^2 + (s_1 -1)^2 + (s_2 -1)^2 $} 
%			\STATE {$\theta_G$}{$\frac{\delta \mathcal{L}_G}{\delta \theta_G}$}  \Comment{Update generator}
%			\STATE {$\theta_D$}{$\frac{\delta \mathcal{L}_D}{\delta \theta_D}$}  \Comment{Update generator}
%		\EndFor	
%	\end{algorithmic}
%\end{algorithm}
